A Fast Unified Model for Parsing and Sentence Understanding

### 2016-05-30 writing/hard_stack_paper/paper.tex
Incorporating Cheng/Lapata result update.

Because this paper aims to introduce a general purpose model for sentence encoding, we do not pursue the use of soft attention \citep{bahdanau2014neural,rocktaschel2015reasoning}, despite its demonstrated effectiveness on the SNLI task.\footnote{Attention based models like \citet{rocktaschel2015reasoning} and the unpublished \citet{cheng2016long} have shown accuracies as high as 89.0\% on SNLI, but are more narrowly engineered to suit the task, and do not yield sentence encodings.} However, we expect that it should be possible to productively combine our model with soft attention to reach state-of-the-art performance.

>>>>

Because this paper aims to introduce a general purpose model for sentence encoding, we do not pursue the use of soft attention \citep{bahdanau2014neural,rocktaschel2015reasoning}, despite its demonstrated effectiveness on the SNLI task.\footnote{Attention based models like \citet{rocktaschel2015reasoning,wang2015learning} and the unpublished \citet{cheng2016long} have shown accuracies as high as 86.1\% on SNLI, but are more narrowly engineered to suit the task, and do not yield sentence encodings.} However, we expect that it should be possible to productively combine our model with soft attention to reach state-of-the-art performance.
